Roster Review (Generic)

### 2019-06-09 rosterReview_generic.Rmd
Latest projections and rosters

```{r}
#TODO abstract some of these views
rosters %>% 
  mutate(zar = round(zar)) %>% 
  filter((team == 'Free Agent' & zar >=0) | (grepl("Plouffe",team) & zar < 0)) %>% 
  ggplot(aes(x=team,y=zar,color=type)) +
  geom_jitter(aes(text=glue("{name_full} - {display_position}", color=type))) +
  coord_flip() -> pa

@@

rosters %>% 
  filter((team == 'Free Agent' & zar >=0) | (grepl("Plouffe",team) & zar < 0)) %>% 
  arrange(zar %>% desc) %>% 
  select(name_full, positions, type, zar) %>% 
  View()
```

>>>>

```{r}
#TODO abstract some of these views
rosters %>% 
  mutate(zar = round(zar)) %>% 
  filter((team == 'Free Agent' & zar >=0) | (grepl("Plouffe",team) & zar < 2)) %>% 
  ggplot(aes(x=team,y=zar,color=type)) +
  geom_jitter(aes(text=glue("{name_full} - {display_position}", color=type))) +
  coord_flip() -> pa

@@

rosters %>% 
  filter((team == 'Free Agent' & zar >=0) | (grepl("Plouffe",team) & zar < 2)) %>% 
  arrange(zar %>% desc) %>% 
  select(name_full, positions, type, zar) %>% 
  View()
```
